Response to referee

### 2024-04-30 paper/article_jos.qmd
submitted article

In the section we discuss the applicability of the presented methods to other frequencies (@sec-other-freq) and some limits of the presented methods (for example sensibility to outliers like COVID-19, @sec-out-covid) .

>>>>

In the section we discuss the applicability of the presented methods to other frequencies (@sec-other-freq) and some limits of the presented methods (for example sensitivity to outliers like COVID-19, @sec-out-covid) .

### 2024-04-30 paper/article_jos.tex
submitted article

In the section we discuss the applicability of the presented methods to
other frequencies (section~\ref{sec-other-freq}) and some limits of the
presented methods (for example sensibility to outliers like COVID-19,
section~\ref{sec-out-covid}) .

>>>>

In the section we discuss the applicability of the presented methods to
other frequencies (section~\ref{sec-other-freq}) and some limits of the
presented methods (for example sensitivity to outliers like COVID-19,
section~\ref{sec-out-covid}) .

### 2024-04-30 paper/resp_referee.qmd
submitted article

---
title: "Response to referee"
# format: docx
format: pdf
lang: en-GB  
---

@@

@@

*This sections was simplified*

@@

@@

*More explanation are added to this section*

@@

@@

*Indeed, the formula are corrected*

@@

*All the section was rewritten to be clearer*

@@

*All the code will be in a github repository*

@@

*The modelled of the input time series is now describe more precisely in section 2 (previous section 1).* 
*$TC_t$ is here considered as deterministic*

@@

*The notation is simplified and unified and the equations/notations clarified.*
*The matrix $D$ is needed to see the equivalence with symmetric filter/DAF (clarified in the text).*

@@

*It was added in the beginning of new sections 3 and 4 than the bandwidth is fixed.* 
*Nearest neighbour bandwidth was added in supplemental material but it doesn't improve the results in therm of phase shift.* 
*One explanation could be that the bias is higher with LC/QL methods (we model linear trend using higher bandwidth) and for other methods (e.g. DAF) that the revisions to the final symmetric filters are higher.*

@@

*A lecture note is added*

@@

*Those sections are now numbered*

@@

*Bibliography added and the R icon was removed*

@@

@@

*Figures are now black and white a scaled gray legend.*
*In some of them, there are indeed a lot of information with several labels, but the goal is not to be able to read all the details of all the lines but to see the general behaviour of the filters (for example if the implicit forecasts seem relevant or not)*

@@

*We try to clarify in the section associated to the proposed methods: all the functions mentioned are already in rjd3filters.*
*The local parametrisation is not directly in the package but can be easily implemented (especially because the code is available): the variance estimator is in the package but not the moving-averages associated to slope/concavity estimators (which can be easily derived)*

@@

*This was clarified in the article, for example in the introduction the text was changed with "the X-11 decomposition method (used in X-13ARIMA-SEATS)"*

@@

*More explanation with the reference in parentheses*

@@

*Table 2 was removed*

@@

*This table was removed but to answer your question the criteria comes from the decomposition of the mean squared error into four quantities*

@@

*See previous comment: it was added in supplemental material*

@@

*This section was rewrite to make it clearer.*

@@

*Quarterly series with simulated data are added in supplemental material, a new section was added to discuss the use of the methods with different periodicities*

@@

*The definition of phase-shift was clarified in*

@@

*A reading note is added to figure 5 to improve its reading*

@@

*A lecture note is added in the tables and more explanations are added to the text*

@@

*Quarterly series with simulated data are added in supplemental material, a new section was added to discuss the use of the methods with different periodicities*

@@

*We try to clarify the contribution in the abstract, introduction and in the beginning of sections 2 and 3*

@@

*A new section was added with an example around Covid19 and some possible solutions for outliers*

@@

*The quote was removed*

>>>>

---
title: "Response to referee"
# format: docx
format: 
  pdf:
    geometry:
      - top=2cm
      - bottom=2cm
      - left = 2.5cm
      - right = 2.5cm
lang: en-GB  
---

@@

Thank you for reviewing our paper and thank you for your helpful comments and suggestions.
Below are our responses (*in italics*) to your comments and suggestions:

@@

*This sections was simplified.*

@@

*The section 1.3.2 was removed: it's not central to the paper, and it would have made the reading more cumbersome to go into the details of the notations. Table 2 has also been removed.*

@@

*More explanation are added to this section.*

@@

*Fixed.*

@@

*Indeed, the formula are corrected.*

@@

*All the section was rewritten to be clearer.*

@@

*All the code will be in a github repository.*

@@

*The model of the input time series is now describe more precisely in section 2 (previous section 1).* 
*$TC_t$ is here considered as deterministic (clarified in the text).*

@@

*The notation is simplified and unified and the equations/notations clarified.*
*The matrix $D$ is needed to show the equivalence with symmetric filter/DAF (clarified in the text).*

@@

*It was added in the beginning of new sections 3 and 4 that the bandwidth is fixed.* 
*Nearest neighbour bandwidth was added in supplemental material but it doesn't improve the results in therm of phase shift.* 
*One explanation could be that the bias is higher with LC/QL methods (we model linear trend using higher bandwidth) and for other methods (e.g. DAF) that the revisions to the final symmetric filters are higher.*

@@

*A lecture note is added below the figure to explain how to read the panels.*
*The ratio $I/C$ is no longer mentioned in the caption but some details are added in the figure note.*

@@

*Those sections are now numbered.*

@@

*Bibliography added and the R icon was removed.*

@@

*Lecture notes were added to all tables and figures.*

@@

*Figures are now black and white with a scaled grey legend.*
*In some of them, there are indeed a lot of information with several labels, but the goal is not to be able to read all the details of all the lines but to see the general behaviour of the filters (for example if the implicit forecasts seem relevant or not).*

@@

*We try to clarify in the section associated to the proposed methods: all the functions mentioned are already in rjd3filters.*
*The local parametrisation is not directly in the package but can be easily implemented (especially because the code is available): the variance estimator is in the package but not the moving-averages associated to slope/concavity estimators (which can be easily derived).*

@@

*This was clarified in the article, for example in the introduction the text was changed with "the X-11 decomposition method (used in X-13ARIMA-SEATS)".*

@@

*More explanation are added with a clearer contribution of the reference to Pierce (1980).*

@@

*Table 2 was removed.*

@@

*This table was removed but to answer your question the criteria comes from the decomposition of the mean squared error into four quantities.*

@@

*See previous comment: it was added in supplemental material.*

@@

*This section was rewriten to make it clearer.*

@@

*Quarterly series with simulated data are added in supplemental material, a new section was added to discuss the use of the methods with different periodicities.*

@@

*The corresponding text was rewritten to clarify the definition of phase-shift used in this paper.*

@@

*A reading note is added to figure 5 to improve its reading.*

@@

*A lecture note is added in the table and more explanations are added to the text.*

@@

*Quarterly series with simulated data are added in supplemental material, a new section (just before the conclusion) was added to discuss the use of the methods with different periodicities.*

@@

*We try to clarify the contribution in the abstract, introduction and in the beginning of sections 2 and 3.*

@@

*A new section was added with an example around Covid19 and some possible solutions for outliers.*

@@

*The quote was removed.*
